---
title: "Johns Hopkins University - Data Viz Certification Final Project"
runtime: shiny
output:
  flexdashboard::flex_dashboard: null
  orientation: rows
  vertical_layout: fill
  source_code: embed
  theme: cosmo
resource_files:
- nobel.rds
---

```{r setup, include=FALSE}

#####Make sure you load any required packages.

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(magrittr)
library(openxlsx)
library(readxl)
library(writexl)
library(reshape2)
library(skimr)
library(janitor)
library(lubridate)
library(ggthemes)
library(plotly)
library(DT)
library(rsconnect)
library(timetk)
library(wordcloud2)
library(ggside)
library(ggthemes)
library(ggforce)
library(gganimate)
library(treemap)
library(shiny)
library(tidyquant)

```

```{r, include=FALSE} 

readRDS("nobel.rds") -> nobel

```

# Data Table

## Column {data-width="1000"}

```{r}

DT::datatable(nobel, 
              extensions = "Buttons",
              options = list(pageLength = 100, 
                             scrollY= TRUE,
                             dom = "Blfrtip",
                             buttons = c("copy", "csv", "excel", "pdf")))


```

# Page 1

### Chart A *1. Histogram: distributions of winners by age.*



```{r data_1, echo = FALSE}
nobel %>% 
  dplyr::select(age_get_prize) -> number_1_data


####make sure you call the data so it will display in your report

number_1_data %>% 
  ggplot2::ggplot(mapping = aes(x = age_get_prize)) +
  ggplot2::geom_histogram(fill = "lightblue") +
  ggplot2::theme_classic() +
  ggplot2::labs(title = "Histogram: distributions of winners by age",
                x = "Age get Prize",
                y = NULL) -> number_1_fig

number_1_fig

```

Page 2
======
  
### Chart B *2. Bar charts: winners by Top 10 university*


```{r data_2, echo = FALSE}
nobel %>% 
  dplyr::select(name_of_university) %>% 
  dplyr::count(name_of_university) %>% 
  dplyr::arrange(desc(n)) %>% 
  dplyr::slice_head(n = 10) -> number_2_data


####make sure you call the data so it will display in your report

number_2_data %>% 
  dplyr::slice(n = -1) %>% 
  ggplot2::ggplot(mapping = aes(y = reorder(name_of_university, n), x = n)) +
  ggplot2::geom_bar(stat = "identity",
                    mapping = aes(fill = name_of_university),
                    show.legend = FALSE) +
  ggthemes::theme_tufte() +
  ggplot2::labs(title = "Bar charts: winners by Top 10 university",
                x = "Number of Nobel Prize", 
                y = "Name of University") +
  ggplot2::geom_text(mapping = aes(label = n), hjust = "inward") +
  ggplot2::theme(plot.title = element_text(size = 13)) -> number_2_fig

number_2_fig



```

Page 3
======

### Chart C  *3. Pie plot: average age of winners by category.*


```{r data_3, echo = FALSE}
nobel %>% 
  dplyr::select(gender, age, category) %>% 
  dplyr::group_by(category) %>% 
  dplyr::summarise(mean = mean(age)) %>% 
  dplyr::mutate(mean = round(mean, 0)) %>% 
  dplyr::arrange(desc(mean)) -> number_3_data


number_3_data %>% 
  ggplot2::ggplot(mapping = aes(x = desc(reorder(category, mean)), y = mean, fill = category)) +
  ggplot2::geom_bar(stat = "identity") +
  ggplot2::coord_polar() +
  ggplot2::geom_text(mapping = aes(label = paste0(category, " - ", mean))) +
  ggplot2::scale_y_continuous(labels = scales::number) +
  ggplot2::theme_void() +
  ggplot2::theme(legend.position = "none")+
  ggplot2::labs(title = "Average age of Winners by Category") -> number_3_fig


number_3_fig

```


Page 4
======

### Chart D  *4. Line Plot: Number of Nobel Prize received by Gende*


```{r data_4, echo = FALSE}
nobel %>% 
  dplyr::select(gender, year) %>% 
  dplyr::group_by(gender, year) %>% 
  dplyr::count() %>% 
  dplyr::ungroup() %>% 
  dplyr::rename(Gender = gender)-> number_4_data
  
number_4_data %>% 
  ggplot2::ggplot(mapping = aes(x = year, y = n, group = Gender)) +
  ggplot2::geom_line(mapping = aes(color = Gender)) +
  ggplot2::labs(title = "Number of Nobel Prize received by Gender",
                y = "Number of Nobel Prize",
                x = "Year") +
  ggplot2::theme_classic() +
  ggplot2::scale_color_discrete(breaks = c("male", "female"),
                                labels = c("Male", "Female")) -> number_4_fig



number_4_fig

```


Page 5
======

### Chart E  *5. Bar Plot: by Countries that produced the Nobel Prize Winner the most*


```{r data_5, echo = FALSE}
nobel %>% 
  dplyr::group_by(country_of_university) %>% 
  dplyr::count() %>% 
  dplyr::filter(country_of_university != "") %>% 
  dplyr::arrange(desc(n))-> number_5_data


number_5_data %>% 
  ggplot2::ggplot(mapping = aes(x = n, y = reorder(country_of_university, n))) +
  ggplot2::geom_bar(stat = "identity", fill = "lightgreen") +
  ggplot2::geom_text(mapping = aes(label = n), hjust = "inward", color = "tomato1") +
  ggplot2::labs(title = "Bar Plot: by Countries that produced the Nobel Prize Winner the most",
                x = NULL,
                y = NULL) +
  ggthemes::theme_tufte() +
  ggplot2::theme(axis.ticks.x = element_blank(),
                 axis.text.x = element_blank())-> number_5_fig

number_5_fig


```


Page 6
======

### Chart F  *6. Correlation between year and age*


```{r data_6, echo = FALSE}

nobel %>% 
  ggplot2::ggplot(mapping = aes(x = year, y = age)) +
  ggplot2::geom_point(size = 5, alpha = 0.2, color = "blue") +
  ggthemes::theme_stata() +
  ggplot2::labs(title = "Correlation between the Year and Age",
                subtitle = "Density of points shows the age trend of Nobel Prize",
                x = "Year", 
                y = "Age") +
  # ggforce::geom_mark_ellipse(mapping = aes(group = year), 
  #                            linetype = "dashed",
  #                            alpha = 0.2,
  #                            color = "grey50") +
  
  ggplot2::annotate("rect", xmin = 2012, xmax = 2020, ymin = 20, ymax = 30, alpha = 0.2, fill = "red") +
  ggplot2::annotate(geom = "curve", x = 2000, xend = 2005, y = 15, yend = 20, size = 1.5,
                    curvature = 0.2, arrow = arrow(length = unit(4, "mm"))) +
  ggplot2::annotate(geom = "text", x = 1995, y = 25, label = "First 20's Nobel Prize", color = "red") +
  ggplot2::annotate(geom = "curve", x = 1975, xend = 2020, y = 90, yend = 70, size = 1.5, color = "red",
                    curvature = 0, arrow = arrow(length = unit(4, "mm"))) +
  ggplot2::annotate(geom = "text", x = 2000, y = 79, label = "Getting Younger", size = 5, color = "yellow") +
  ggplot2::geom_rug(position = "jitter", size = 0.2, alpha = 0.3) -> number_6_fig

number_6_fig

```

Page 7
======

### Chart G  *7. Tree Map by countries that produced the most Nobel Prize Winner*

```{r data_7, echo = FALSE}
nobel %>% 
  dplyr::group_by(country_of_university) %>% 
  dplyr::count() %>%
  dplyr::arrange(desc(n)) %>%
  data.frame() %>% 
  dplyr::slice(n = -2) %>% 
  dplyr::slice_head(n = 50) %>% 
  dplyr::rename("Tree Map by countries that produced the most Nobel Prize Winner" = n) -> number_7_data

treemap::treemap(number_7_data,
                 index = "country_of_university",
                 vSize = "Tree Map by countries that produced the most Nobel Prize Winner",
                 type = "index") 

```

Page 8
======

### Chart G  *8. 3 ways Plot*

```{r data_8, echo = FALSE}
nobel %>% 
  ggplot2::ggplot(mapping = aes(x = year, y = age)) +
  ggplot2::geom_point(mapping = aes(color = gender),
                      size = 2,
                      alpha = 0.5) +
  ggplot2::annotate("rect", xmin = 2012, xmax = 2020, ymin = 20, ymax = 30, alpha = 0.2, fill = "red") +
  ggplot2::annotate(geom = "curve", x = 2000, xend = 2005, y = 15, yend = 20, size = 1.5,
                    curvature = 0.2, arrow = arrow(length = unit(4, "mm"))) +
  ggplot2::annotate(geom = "text", x = 1995, y = 25, label = "First 20's Nobel Prize", color = "red") +
  ggplot2::annotate(geom = "curve", x = 1975, xend = 2020, y = 90, yend = 70, size = 1.5, color = "red",
                    curvature = 0, arrow = arrow(length = unit(4, "mm"))) +
  ggplot2::annotate(geom = "text", x = 2000, y = 79, label = "Getting Younger", size = 5, color = "yellow") +
  ggplot2::geom_rug(position = "jitter", size = 0.2, alpha = 0.3) +
  ggside::geom_xsidedensity(mapping = aes(y = ggplot2::after_stat(density), fill = category),
                            alpha = 0.5,
                            position = "stack") +
  ggside::geom_ysidefreqpoly(color = "red") +
  ggside::geom_ysidehistogram(fill = "blue",
                              alpha = 0.5) +
  tidyquant::scale_color_tq() +
  tidyquant::scale_fill_tq() +
    tidyquant::theme_tq() +
  ggplot2::theme(ggside.panel.scale.x = 0.4,
                 ggside.panel.scale.y = 0.4) +
  ggplot2::scale_color_manual(values = c("red","blue")) +
  ggplot2::labs(title = "Main Plot: Correlation between the Year and Age",
                subtitle = "X - Side Plot: Density Plot by Category\nY - Side Plot: Histogram by Age of Nobel Winners",
                x = "Year",
                y = "Age") +
  ggplot2::theme(plot.title = element_text(size = 12)) -> number_8_fig

number_8_fig

```


Page 9
======

### Chart G  *9. Radar Chart*

```{r data_9, echo = FALSE}
nobel %>% 
  dplyr::group_by(category) %>% 
  dplyr::count()  -> number_9_data


number_9_data %>% 
  ggplot2::ggplot() +
  ggplot2::geom_hline(mapping = aes(yintercept = y),
                      data.frame(y = c(0:6) * 50),
                      color = "lightgrey") +
  ggplot2::geom_col(mapping = aes(x = reorder(str_wrap(category, 6), n),
                                  y = n,
                                  fill = n),
                    position = "dodge2",
                    show.legend = TRUE,
                    alpha = 0.9) +
  ggplot2::geom_point(mapping = aes(x = reorder(str_wrap(category, 6), n),
                                    y = n),
                      size = 3,
                      color = "gray12") +
  ggplot2::geom_segment(mapping = aes(x = reorder(str_wrap(category, 6), n),
                                      y = 0,
                                      xend = reorder(str_wrap(category, 6), n),
                                      yend = 250),
                        linetype = "dashed",
                        color = "gray12") +
  ggplot2::coord_polar() +
  ggplot2::annotate(x = 6,
                    y = 100,
                    label = "Total number of awarded",
                    geom = "text",
                    angle = -34,
                    size = 3.25,
                    vjust = 1) +
  ggplot2::annotate(x = 7,
                    y = 51,
                    label = "50",
                    geom = "text") +
  ggplot2::annotate(x = 7,
                    y = 101,
                    label = "100",
                    geom = "text") +
  ggplot2::annotate(x = 7,
                    y = 151,
                    label = "150",
                    geom = "text") +
  ggplot2::annotate(x = 7,
                    y = 201,
                    label = "200",
                    geom = "text") +
  ggplot2::annotate(x = 7,
                    y = 251,
                    label = "250",
                    geom = "text") +
  ggplot2::scale_y_continuous(limits = c(-100, 300),
                              expand = c(0, 0),
                              breaks = c(0, 50, 100, 150, 200, 250)) +
  ggplot2::scale_fill_gradientn("Number of Awarded",
                                colors = c("#6C5B7B","#C06C84","#F67280","#F8B195")) +
  ggplot2::guides(fill = guide_colorsteps(barwidth = 15, barheight = 0.5, title.position = "top", title.hjust = 0.5)) +
  ggplot2::theme(axis.title = element_blank(),
                 axis.ticks = element_blank(),
                 axis.text.y = element_blank(),
                 axis.text.x = element_text(color = "gray12"),
                 legend.position = "bottom") +
  ggplot2::labs(title = "This visualization shows the category's awarded portion") +
  ggplot2::theme(panel.background = element_rect(fill = "white", color = "white")) -> number_9_fig
  

number_9_fig

```
